---
title: "Overview of the Example Package"
author: "John Owens"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of the Example Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r initialize, echo=FALSE, include=FALSE}
library(dplyr)
library(readr)
library(tidyr)
library(maps)
library(Second)
```

This vignette gives instructions about how to use the Second package to analyze data from Fatality Analysis Reporting System (FARS) (www-fars.nhtsa.dot.gov).

## Read a datafile from the working path.
```{r readSimple}
fars_read(system.file("extdata","accident_2013.csv.bz2",package="Second"))

```
## Create an appropriate file name.
```{r makeName}
make_filename(2013)
```
## Create multiple years of data.

A list of tbls representing the year, Month data extracted from the given set of years from the Fatality Analysis Reporting System.

```{r manyYears,message=FALSE, warning=FALSE}
setwd(system.file("extdata", package = "Second"))
fars_read_years(2013:2015)

```
## Summarize by years.

Creates a country-wide summary table of the number of fatal accidents by month by year for a given set of years.

```{r SummaryYear, message=FALSE, warning=FALSE}
setwd(system.file("extdata", package = "Second"))
fars_summarize_years(2013:2015)

```

## Sumarize by monthy by years for a given state.

Creates a summary table of the number of fatal accidents by month by year for a given set of years for a given state.

```{r byStae, message=FALSE, warning=FALSE}
setwd(system.file("extdata", package = "Second"))
fars_map_state(1,2013)

```

